\documentclass[letterpaper,10.9pt]{article}

% Packages and Customizations
\usepackage[left=0.6in, right=0.6in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{parskip}
\pagestyle{empty}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true, 
	urlcolor=blue,
	pdfnewwindow=true
}
\usepackage{multicol}
\usepackage{setspace}
\setstretch{1}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

% Document Content
\begin{document}
	\begin{center}
		\textbf{\huge Abdul Aziz Mohammed}\\
		\smallskip
		(737) 336-1822 \textbar\ Dallas, Texas \textbar\ 
		abdul.aziz.mohammed@outlook.com \\
		\href{https://www.linkedin.com/in/abdulaziz-mohammed0}{linkedin.com/in/abdulaziz-mohammed0} \textbar\ \href{https://github.com/abdul-aziz-mohammed}{github.com/abdul-aziz-mohammed}
	\end{center}
	
	\vspace{-2mm}
	\section*{\textbf{PROFESSIONAL SUMMARY}}
	Computer Science student poised to contribute advanced expertise in cloud computing, AI, and machine learning to dynamic tech environments. Recognized for driving innovative solutions and strategic data-driven decision-making, merging academic rigor with practical experience in consulting and project leadership.
	
	\vspace{-2mm}
	\section*{\textbf{EDUCATION}}
	\textbf{Bachelor of Science in Computer Science} \hfill \textnormal{Expected Graduation: Dec 2024} \\
	The University of Texas at Dallas \hfill \textnormal{Richardson, Texas} \\
	\textbf{Organizations:} Association for Computing Machinery (ACM), AWS Cloud Club, AIS UTD, Consulting Leadership \& Development Society (CLDS)
	
	\vspace{-2mm}
	\section*{\textbf{TECHNICAL SKILLS}}
	\vspace{-3mm}
	\begin{multicols}{2}
		\begin{itemize}
			\item \textbf{AI and Machine Learning:} Deep Learning, NLP, ML Algorithms
			\item \textbf{Programming Languages:} Python, Java, JavaScript
			\item \textbf{Cloud Technologies:} AWS, Azure, Docker
		\end{itemize}
		\columnbreak
		\begin{itemize}
			\item \textbf{Data Science:} Data Analysis, Jupyter Notebooks
			\item \textbf{Software Development:} Full-stack Development, Agile Methodologies
			\item \textbf{Databases:} MySQL, PostgreSQL
		\end{itemize}
	\end{multicols}
		
	\vspace{-6mm}
	\section*{\textbf{WORK EXPERIENCE}}
	\textbf{Digital Transformation Consultant} \hfill \textnormal{September 2022 - Present} \\
	Self-Employed, Contracted for AMZ Infotech \textbar\ Remote
	\vspace{-2mm}
	\begin{itemize}
		\item Led AI strategy development and execution, focusing on NLP and ML applications, resulting in a 18\% improvement in operational efficiency and customer engagement.
		\item Engineered custom AI solutions, including ML-driven predictive models and NLP-based chatbots, increasing customer satisfaction by 23\%.
		\item Performed data analysis using AI tools, uncovering key insights that influenced business strategies, leading to a 32\% growth in market reach.
		\item Automated critical processes using ML algorithms, cutting operational costs by 12\% and boosting efficiency.
		\item Advised on AI ethics and compliance, ensuring responsible and regulation-compliant AI implementation.
		\item Orchestrated cloud migration for enhanced data management and AI integration, improving system performance by 35\%.
	\end{itemize}
	
	\vspace{-2mm}
	\section*{\textbf{PROJECTS}}
	\textbf{Flood Risk Prediction for Property Owners (Baltimore County)} \\
	\href{https://github.com/abdul-aziz-mohammed/flood-risk-prediction-for-property-owners}{github.com/abdul-aziz-mohammed/flood-risk-prediction-for-property-owners} \\
	Initiated and developed a comprehensive flood risk prediction model focused on Baltimore County, integrating geospatial analysis and environmental data. This personal project involved:
	\begin{itemize}
		\vspace{-1mm}
		\item Utilizing Python libraries such as Geopandas, Rasterio, and CatBoost for spatial analysis and machine learning.
		\item Analyzing and merging datasets including property assessments and flood probability data.
		\item Developing a predictive model that accurately assesses flood risks for properties, employing advanced statistical methods and data visualization for effective communication of results.
	\end{itemize}
	
	\vspace{-1mm}
	\textbf{DynaFit} \\
	\href{https://github.com/abdul-aziz-mohammed/dynafit}{github.com/abdul-aziz-mohammed/dynafit} \\
	Spearheaded the development of 'DynaFit', a full-stack fitness application, focusing on user engagement and health optimization. Key features and accomplishments include:
	\begin{itemize}
		\vspace{-1mm}
		\item Engineered a robust backend using Express.js and integrated AWS services for scalable infrastructure.
		\item Implemented advanced features like dynamic workout and diet generators, leveraging React for a seamless user experience.
		\item Developed user authentication and profile management modules to enhance security and personalization.
	\end{itemize}
	
	\vspace{-2mm}
	\section*{\textbf{RELEVANT COURSEWORK}}
	\vspace{-2mm}
	\begin{multicols}{2}
		\begin{itemize}
			\item Advanced Algorithm Design
			\item Digital Logic \& Computer Design
			\item Database Systems
		\end{itemize}
		\columnbreak
		\begin{itemize}
			\item Project Management
			\item Data Structures
		\end{itemize}
	\end{multicols}
	
\end{document}
